\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.5in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.1in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure PDF is ATS friendly
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & \textbf{\small #2} \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Zahra Khatti} \\ \vspace{1pt}
    11 Duh Drive, Bethlehem, PA 18015 \\ \vspace{1pt}
    \small  \href{mailto:khatti.zahra@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{khatti.zahra@gmail.com}} ~ 
    \href{https://linkedin.com/in/zahra-khatti}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/zahra-khatti}} ~
    \href{https://github.com/zahrakhatti}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/zahrakhatti}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small
Highly motivated and mathematically oriented Ph.D. student in Industrial and Systems Engineering specializing in fairness in machine learning and nonlinear optimization. Experienced in designing fairness-aware prediction models with provable guarantees by formulating constraints on smooth nonconvex surrogates. Strong background in non-convex analysis, optimization theory, and statistical learning. Skilled in implementing advanced algorithms for large-scale constrained optimization and developing neural network models using PyTorch.

%-----------SKILLS-----------
\section{Skills}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \textbf{Mathematical:} Non-convex analysis, Linear algebra, Optimization
  \item \textbf{Computational:} Python, PyTorch, Gurobi, AMPL, GAMS, R, Git
\end{itemize}
\end{multicols}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lehigh University}{Aug. 2023 -- Present}
      {Ph.D. in Industrial and Systems Engineering}{Bethlehem, PA}
      \resumeItemListStart
        \resumeItem{Advisors: \href{https://coral.ise.lehigh.edu/frankecurtis}{Prof. Frank E. Curtis}, \href{https://coral.ise.lehigh.edu/danielprobinson}{Prof. Daniel P. Robinson}}
        \resumeItem{Research Focus: Fairness in machine learning through constraint-based optimization.}
      \resumeItemListEnd

    \resumeSubheading
      {Sharif University of Technology}{2019 -- 2022}
      {Master of Science in Industrial Engineering, Economic and Social Systems}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Advisor: \href{https://www.ie.sharif.ir/en/-faculty}{Prof. Farhad Kianfar}}
        \resumeItem{Dissertation: Customer Segmentation and Migration Pattern Modeling Based on Loyalty.}
      \resumeItemListEnd

    \resumeSubheading
      {K.N. Toosi University of Technology}{2015 -- 2019}
      {Bachelor of Science in Industrial Engineering}{Tehran, Iran}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item  \href{https://arxiv.org/abs/2505.15788}{Zahra Khatti, Daniel P Robinson, and Frank E Curtis. Fair supervised learning through constraints on smooth nonconvex unfairness-measure surrogates. arXiv preprint arXiv:2505.15788, 2025.}
    \resumeItemListStart
        \resumeItem{Designed fairness-aware neural networks in PyTorch with constraint-based optimization.}
        \resumeItem{Applied Sequential Quadratic Programming (SQP) for solving large-scale constrained ML problems.}
        \resumeItem{Conducted mathematical analysis of fairness guarantees.}
    \resumeItemListEnd
\end{itemize}

%-----------SELECTED PROJECTS-----------
\section{Selected Projects}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Review of Uncertainty Quantification for Deep Learning Models}{2023}
%       {Lehigh University}{Bethlehem, PA}
%       \resumeItemListStart
%         \resumeItem{Reviewed and analyzed techniques for uncertainty quantification under limited data conditions.}
    %   \resumeItemListEnd

    % \resumeSubheading
    %   {Business Process Simulation Models from Event Logs}{2020}
    %   {Sharif University of Technology}{Tehran, Iran}
    %   \resumeItemListStart
    %     \resumeItem{Developed models for automated discovery of business process simulation models from event logs.}
    %   \resumeItemListEnd

    \resumeSubheading
      {Multi-Stage Financial Planning Problem}{2020}
      {Sharif University of Technology}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Optimized financial planning using scenario reduction and nested decomposition.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Assessment and Layout Planning of Wagon Generator Industrial Units}{2017}
    %   {K.N. Toosi University of Technology}{Tehran, Iran}
    %   \resumeItemListStart
    %     \resumeItem{Conducted layout planning to improve operational efficiency in industrial units.}
    %   \resumeItemListEnd
  % \resumeSubHeadingListEnd

%-----------SELECTED COURSES-----------
\section{Selected Courses}
\begin{multicols}{2}
\small
  \begin{itemize}[leftmargin=0.15in, label={}]
    \setlength{\itemsep}{0.5pt}
    \item Statistical Machine Learning
    \item Continuous Optimization
    \item Stochastic Processes
  \end{itemize}
  \columnbreak
  \begin{itemize}[leftmargin=0.15in, label={}]
    \setlength{\itemsep}{0.5pt}
    \item Project Management and Control
    \item Decision Management and Analysis
  \end{itemize}
\end{multicols}

%-----------VOLUNTEER WORK-----------
\section{Volunteer Work}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MOPTA Conference Co-chair}{2025 (ongoing)}
      {Lehigh University}{Bethlehem, PA}
      \resumeItemListStart
        \resumeItem{Co-organizing the 2026 MOPTA conference; coordinating speakers, sessions, and logistics.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduation Ceremony Organizer}{2019}
      {K.N. Toosi University of Technology}{Tehran, Iran}

    \resumeSubheading
      {Executive Board Member}{2016--2017}
      {Scientific Association, K.N. Toosi University}{Tehran, Iran}

  \resumeSubHeadingListEnd
\end{document}
